A Large-Scale Study of the Use of Eval in R

### 2020-08-25 inst/paper/main.tex
V

We have selected the TOP \CorpusPackages packages based on the number of reverse
dependencies, \ie how many other packages depend on them\footnote{Extracted from
  package metadata using builtin function}. Using this criterion helps us to
choose popular packages which in general should be of a better quality and
should have better code coverage. The resulting set has \summary{CorpusRevdeps}
reverse dependencies (min / mean / max) and consists of \CorpusRCodeRnd lines of
R code and \CorpusNativeCodeRnd lines of native code (C/C++/Fortran).
Figure~\ref{fig:corpus} shows these packages, the size of the dots reflects the
project's size in lines of code including both R and native code, the x-axis
indicates the expression code coverage in percents and the y-axis gives the
number of reverse dependencies in log scale. Dotted lines indicate means.
Packages with over \CorpusEvalsPackageTreshold eval call sites are annotated.

@@

There are three sources of runnable code in a R package. Next to the package
\emph{tests}, there are: \emph{examples} and \emph{vignettes}. Examples are R
code snippets extracted from package documentation into scripts file. Vignettes
are long-form guides into package functionality written using
literate-programming style in \LaTeX\xspace or Rmarkdown with chunks of R code
that can be similarly extracted into R scripts. R provides builtin functions for
tangling the embedded code into files.

The selected packages contain \CorpusPackagePrograms programs with
\CorpusPackageProgramsCodeRnd lines of R code. Most programs are examples
(\CorpusExamplesPrograms) with \CorpusExamplesCodeRnd lines of code, followed by
tests (\CorpusTestsPrograms) with \CorpusTestsCodeRnd lines of code and
vignettes (\CorpusVignettesPrograms) with \CorpusVignettesCodeRnd lines of code.

>>>>

We have selected the TOP \CorpusPackages packages based on the number of reverse
dependencies, \ie how many other packages depend on them\footnote{Extracted from
  package metadata using builtin function}. Using this criterion helps us to
choose popular packages which in general should be of a better quality and
should have better code coverage. The resulting set has
\summary{CorpusRevdeps}\footnote{Such triples represent ($min$ / $mean$ /
  $max$)} reverse dependencies and consists of \CorpusRCodeRnd lines of R code
and \CorpusNativeCodeRnd lines of native code (C/C++/Fortran).
Figure~\ref{fig:corpus} shows these packages, the size of the dots reflects the
project's size in lines of code including both R and native code, the x-axis
indicates the expression code coverage in percents and the y-axis gives the
number of reverse dependencies in log scale. Dotted lines indicate means.
Packages with over \CorpusEvalsPackageTreshold eval call sites are annotated.

@@

There are three sources of runnable code in a R package. Next to the package
\emph{tests}, there are also \emph{examples} and \emph{vignettes}. Examples are
R code snippets extracted from package documentation into scripts file.
Vignettes are long-form description of package functionality written using
literate-programming style in \LaTeX\xspace or Rmarkdown with chunks of R code
that can be similarly extracted into R scripts. R provides builtin functions for
tangling the embedded code into files.

The selected packages contain \CorpusPackagePrograms programs with
\CorpusPackageProgramsCodeRnd lines of R code:
%
\begin{compactitem}[$-$]
  \item \CorpusExamplesProgramsRnd examples with \CorpusExamplesCodeRnd
  \summaryrnd{CorpusExamplesCode} lines of code,
  \item \CorpusTestsProgramsRnd tests with \CorpusTestsCodeRnd
  \summaryrnd{CorpusTestsCode} lines of code, and
  \item \CorpusVignettesProgramsRnd vignettes with \CorpusVignettesCodeRnd
  \summaryrnd{CorpusVignettesCode} lines of code.
\end{compactitem}
